---
title: "World best 50 restaurants"
author: "Giuseppe Fumarola"
date: "19/11/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(base)
library(shiny)
library(dplyr)
library(quantmod)
library(leaflet)
library(plotly)
library(tibble)
library(curl)
options(scipen=999)

#load the data

  restaurants <<- read.delim("50_best_restaurants_database.txt", na = "NA")
  icones <<- read.table("icons.txt", quote="\"", comment.char="")


# popups for map

popups <- function() {
  items <<- NULL
  for (i in 1:50) {
    first <- paste("<b>#", restaurants$Ranking[i], "-", restaurants$Restaurant[i], if (!is.na(restaurants$Stars[i])) {strrep("*", restaurants$Stars[i])}, "</b></br>")
    second <- paste(restaurants$City[i], "-", restaurants$Country[i], "</br>")
    third <- paste(restaurants$Description[i], "</br>")
    fourth <- paste("Chef:", restaurants$Chef[i], "</br>")
    fifth <- paste("Website: <a href =", restaurants$Website[i], ">", restaurants$Website[i], "</a>")
    item <- paste(first, second, third, fourth, fifth)
    items <<- c(items, item)
  }}
popups()

# currencies

chartrend <- function() {
  exclist = NULL
  for (i in unique(restaurants$Currency)) {
    exc <- paste("EUR",i, sep = "/")
    exclist <- c(exclist, exc)
  }
  exrates = NULL
  for (i in exclist) {
    rate <- tail(getSymbols(Symbols = i, src = "oanda", from = Sys.Date()-5, auto.assign = FALSE),1)
    exrates <- c (exrates, rate)
  }
  extable <<- data.frame(currency = exclist, rate = exrates)

  menu_curr = c()
  
  for (i in 1:50) {
    if (restaurants$Currency[i] == "EUR") {
      menu_curr <- c(menu_curr, restaurants$Menu[i])
    }
    else {
      rateind <- which(extable$currency == paste("EUR", restaurants$Currency[i], sep = "/"))
      menu_curr <- c(menu_curr, round(restaurants$Menu[i] / extable$rate[rateind]))
    }
  }
  restaurants_new <<- restaurants %>% mutate(menu_loc = menu_curr)
  
  #plot
  chart <<- with(restaurants_new, plot_ly ( 
    x = Ranking, y = menu_curr, type = "scatter", mode = "markers", 
    color = as.factor(Stars), marker = list(size = 12, color = "pal")) 
    %>%
      layout(title = "50 best restaurants 2019", 
             xaxis = list(title = "Ranking"), 
             yaxis = list(
               title = "Full Tasting Menu Price (EUR)"),
             legend=list(title=list(text='Michelin stars')))
    %>% add_trace(text = restaurants_new$Restaurant, showlegend = F))
}

chartrend()

```

## Introduction

This presentation will display the location of the world best 50 restaurants, based on the ranking of 2019. </br> </br>
In the next slide, you can interact with the map to receive detailed information on specific restaurants. </br> </br>
You can also move the slider to choose which and how many restaurants to display on the map, based on their ranking.

## Interactive Map

```{r map}
inputPanel(
   sliderInput("slider",
                  "Ranking:",
                  min = 1,
                  max = 50,
                  value = c(1,50))
)

renderLeaflet({
  rmin = input$slider[1]
    rmax = input$slider[2]
    icone = list(iconUrl = icones$V1[rmin:rmax], iconWidth = 30, iconHeight = 30)
    mappar <<- restaurants %>% leaflet() %>% addTiles() %>% addMarkers(lng = restaurants$Lon[rmin:rmax], lat = restaurants$Lat[rmin:rmax], popup = items[rmin:rmax], icon = icone, clusterOptions = markerClusterOptions(showCoverageOnHover = FALSE))
    mappar
})

```

## Scams or good deals?

The chart displayed in the next slide shows that top ranking restaurants do not necessarily have higher dining expenses, so you could get very good deals! </br> </br>
However, the price for a full tasting menu, drinks excluded, seems to be somehow linked with the numbers of Michelin stars awarded.  </br> </br>
Please note that restaurants part of the best 50 ranking but not reviewed by the Michelin guide have been excluded from the chart.

## Chart

```{r chart, message=FALSE, warning=FALSE}

renderPlotly(chart)

```


